% !TEX root = template.tex

\section{Conclusion}
This study comprehensively characterized the \textit{Lipase/vitellogenin} domain family by integrating PSSM and HMM sequence models, taxonomic distribution analysis, GO term enrichment, and motif identification. These approaches provided a multidimensional perspective on the domain’s biological significance.
The PSSM model proved effective in capturing conserved positional patterns, outperforming the HMM model in most metrics due to its simplicity. However, HMM models remain promising with further optimization and larger training datasets. Taxonomic analysis highlighted the domain's evolutionary importance, particularly within \textit{Mammalia}, with notable clusters in \textit{Rodentia} and \textit{Primates}. These results suggest a conserved role in lipid metabolism and energy regulation.
GO term enrichment emphasized the domain's central role in lipid processing, with significant terms such as \textit{lipoprotein remodeling} and \textit{lipase activity} highlighting its involvement in critical metabolic pathways. Motif analysis further identified conserved patterns in disordered regions, suggesting their role in protein interactions and regulation.
Future efforts should focus on refining computational models and validating the identified motifs experimentally to better understand their molecular mechanisms. Additionally, investigating interactions with other domains and pathways could provide a more complete picture of the domain’s functions.
